### 2023-10-25 paper/draft.tex

What is the formula for $\alpha_i$?  $\mathcal{O}(n)$ algorithm for computing all $\alpha_i$ given an index $\{\pi_i\}_{1\leq i\leq n}$ that sorts $\{f(x_i)_{k+1}\}_{1\leq i \leq n}$?

J: Informally, $\alpha_i$ should be a value between 1 and n-1, denoting the number of instances that have higher estimated confidence than  $f(x_i)_{k+1}$.

@@

>>>>

What is the formula for $\alpha_i$? <TBD> \\

%informal answer: the sum over all losses for samples that are ranked higher than (i), normalized by the rank of i in \pi; but how does its own loss come in? NOT --> maybe it is worthwhile to consider AURC + CE

%O(N^2) version with ascending sort
\begin{align}
    \frac{1}{n} \sum_{i=1}^{n-1} \frac{\sum_{j=i+1}^n\ell([f(x_{i:n})]_{1:k},y_j)}{(n-i)}\label{eq:aurcloss_n2}
\end{align}

$\mathcal{O}(n)$ algorithm for computing all $\alpha_i$ given an index $\{\pi_i\}_{1\leq i\leq n}$ that sorts $\{f(x_i)_{k+1}\}_{1\leq i \leq n}$ in descending order.

%O(N) version with descending sort and assumes zero-based numbering
\begin{align}
    \frac{1}{n} \sum_{i=1}^{n} \frac{1}{i} \sum_{j=0}^{i-1}\ell([f(x_{\pi_j})]_{1:k},y_{\pi_j})
    \label{eq:aurcloss_n}
\end{align}

%if sorted in descending order, then can keep incrementing a partial term containing all losses until i-1; skip first, except for its loss

%version that is very close to the implementation

\section*{Updates 25/10}

\begin{itemize}
    \item $\mathcal{O}(n)$ algorithm implemented and converted to differentiable loss function $\ell_{\mathrm{AURC}}$
    \item batch approximation to test consistency
    \item training with $\ell_{\mathrm{AURC}}$ and test effect of different batch sizes
    \item Literature review on differentiable \AURC TBD
    \begin{enumerate}
        \item \cite{cao2022generalizing} close in spirit, dependent on cost, similarly defines it as a $K+1$ classification problem. 
    \end{enumerate}
\end{itemize}

\section*{Updates 18/10}

From the alphas, which are individual loss weights, we derived \Cref{eq:aurcloss_n2}, which motivates higher weights for samples that are ranked higher than they should be.

% J: as it is implemented in \cite{jaeger2023a}, the alphas/weights denote the number of instances between each contiguous pair of thresholds (in our case based on $f(X)_{k+1}$). 
% If we consider each individual confidence estimate as an integration point, the stepsize between them (i.e. alpha) will be a constant $1/N$.

%WRONG: J: Informally, $\alpha_i$ should be a value between 1 and n-1, denoting the number of instances that have higher estimated confidence than  $f(x_i)_{k+1}$. 
%The most efficient way to obtain is by sorting $f(X)_{k+1}$ in ascending order ( O(nlogn) average case with comparison-based sort such as timsort [default in Python]), then iterate. 
%https://stackoverflow.com/questions/13603042/what-is-the-fastest-way-to-get-a-sorted-unique-list-in-python

@@

\begin{exmp}[simple]\hspace{0.1cm}

    $f(X)_{k+1}$ = [5, 2, 4]

    $\ell([f(X)]_{1:k}, Y)$ = [0, 1, 0]

    $\pi$ = [1,2,0]

\end{exmp}
